R Notebook

### 2017-09-19 doc/RMD/data-comparison.Rmd
update data-comparison to use data within project

```{r}
excel_sheets("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx")
```

@@

```{r sydney_data}
syd <- read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", 
                sheet = "GenAlexBinned", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove whitespace in locus names
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%     # spread data out with individual loci in columns
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, 
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  mutate_if(is.character, trimws) %>% # Trim whitespace forom all character columns
  mutate(Severity = as.numeric(Severity)) %>%
  mutate(Source = ifelse(Source == "", "unk", Source)) %>%
  # slice(-n()) %>% # remove last row
  arrange(Isolate) %>%
  check_data_cromulence
syd
```

@@

```{r sajeewa_data}
column_specification <- cols(
  Individual = col_character(),
  iso_st_mcg_org_loc_yr_hst = col_character(),
  `5-2(F)` = col_integer(),
  `6-2(F)` = col_integer(),
  `7-2(F)` = col_integer(),
  `8-3(H)` = col_integer(),
  `9-2(F)` = col_integer(),
  `12-2(H)` = col_integer(),
  `17-3(H)` = col_integer(),
  `20-3(F)` = col_integer(),
  `55-4(F)` = col_integer(),
  `110-4(H)` = col_integer(),
  `114-4(H)` = col_integer()
)
saj <- read_csv("../Analysis4 ForManu/A2_Copy4 EUR_AUS_forManu.csv", skip = 2, col_types = column_specification) %>%
  select(-1) %>%
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove any whitespace in the locus names
  spread(locus, allele) %>%     # spread data out with individual loci in columns
  separate(iso_st_mcg_org_loc_yr_hst, # Note: this corresponds closer to the initial data
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  mutate_if(is.character, trimws) %>% # Trim whitespace forom all character columns
  mutate(Severity = as.numeric(Severity)) %>%
  arrange(Isolate) %>%
  check_data_cromulence
saj
```

@@

```{r read_excel}
ex <- readxl::read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", sheet = "GenAlex", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove (F) designator
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele)

>>>>

```{r}
excel_sheets(file.path(PROJHOME, "data/raw/2017-02-16_copy-of-binned-genotypes_SE.xlsx"))
```

@@

```{r sydney_data}
syd <- read_excel(file.path(PROJHOME, "data/raw/2017-02-16_copy-of-binned-genotypes_SE.xlsx"),
                sheet = "GenAlexBinned", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove whitespace in locus names
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%     # spread data out with individual loci in columns
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, 
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  mutate_if(is.character, trimws) %>% # Trim whitespace forom all character columns
  mutate(Severity = as.numeric(Severity)) %>%
  mutate(Source = ifelse(Source == "", "unk", Source)) %>%
  # slice(-n()) %>% # remove last row
  arrange(Isolate) %>%
  check_data_cromulence
syd
```

@@

```{r sajeewa_data}
column_specification <- cols(
  Individual = col_character(),
  iso_st_mcg_org_loc_yr_hst = col_character(),
  `5-2(F)` = col_integer(),
  `6-2(F)` = col_integer(),
  `7-2(F)` = col_integer(),
  `8-3(H)` = col_integer(),
  `9-2(F)` = col_integer(),
  `12-2(H)` = col_integer(),
  `17-3(H)` = col_integer(),
  `20-3(F)` = col_integer(),
  `55-4(F)` = col_integer(),
  `110-4(H)` = col_integer(),
  `114-4(H)` = col_integer()
)
saj <- read_csv(file.path(PROJHOME, "data/raw/2017-02-16_binned-genotypes-genalex_SA.csv"), skip = 2, col_types = column_specification) %>%
  select(-1) %>%
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove any whitespace in the locus names
  spread(locus, allele) %>%     # spread data out with individual loci in columns
  separate(iso_st_mcg_org_loc_yr_hst, # Note: this corresponds closer to the initial data
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  mutate_if(is.character, trimws) %>% # Trim whitespace forom all character columns
  mutate(Severity = as.numeric(Severity)) %>%
  arrange(Isolate) %>%
  check_data_cromulence
saj
```

@@

```{r read_excel}
ex <- readxl::read_excel(file.path(PROJHOME, "data/raw/2017-02-16_copy-of-binned-genotypes_SE.xlsx"), sheet = "GenAlex", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove (F) designator
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele)
